% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Mark Betnel}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://markbetnel.com/cv.html}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {physics, education},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://buphy.bu.edu/}{Boston University} \\
  Department of Physics \\
  Boston, MA 02215 
  \end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (401) 461-0268 \\
    Email: & \href{mailto:markbetnel@gmail.com}{\tt markbetnel@gmail.com} \\
    Homepage: & \href{http://www.markbetnel.com/}{\tt http://www.markbetnel.com/} \\
  \end{tabular}
\end{minipage}


%\section*{Personal}
%\begin{itemize}
%\item Born February 1, 1976.
%\end{itemize}


\section*{Education}
\begin{itemize}
  \item \textbf{2005-2010} \\
      Ph.D. 	Physics, 	Boston University\\
	  Thesis: \emph{Computational study of protein folding and assembly in Alzheimer's and Parkinson's diseases} \\
	  Advisor: Brigita Urbanc, Department of Physics, Drexel University 
  \item 	\textbf{2003-2005} \\
	  M.S. 	Physics, University of Rhode Island \\
	  Special study in quantum information theory \\
      Advisor: Gerhard M\"{u}ller 
  \item     \textbf{1999-2002} \\
      M.A. Philosophy, San Francisco State University \\
	  Thesis: \emph{Moral agency in a propaganda system}, Departmental Distinction \\
	  Advisor: Gus Bagakis 
  \item     \textbf{1994-1998} \\
	  B.S. Physics, Harvey Mudd College \\
	  Thesis: \emph{Design of a broadband force feedback seismometer} \\
      Advisor: Greg Lyzenga
\end{itemize}


\section*{Employment}
\begin{itemize}
	\item \textbf{2007-2010} \\
	Research Fellow, Biophysics, Boston University \\  
	Using discrete molecular dynamics to simulate folding, assembly,
	and inhibition of assembly in proteins related to Alzheimer's and
	Parkinson's diseases.  \\
	Skills: Software development, use, and maintenance in C++, Python, VMD, Gromacs, TCL, R.  Biophysics of folding and assembly in disordered proteins.  Effective interaction potentials.  
	\item \textbf{2008-2009} \\
	Graduate Writing Fellow, Boston University \\  
	Courses taught: WR100/WR150 (Freshman writing seminars, first and second semester) \\  
	Skills: Developed curriculum for Popular Science Writing, managed online course content and online peer editing and feedback systems, taught two semesters of writing to college freshmen.  
	\item \textbf{2007-2008} \\
	National Science Foundation GK-12 Fellow, Boston Urban Fellows \\  
	Course taught: High school physics, engineering  \\
	Skills: Curriculum and materials development for high school physics and engineering classes at The Engineering School, a model school in Hyde Park, MA serving a diverse student population.  Developed lecture demonstrations in consultation with the Boston University Physics Department Demo Coordinator.  
	\item \textbf{2005-2008} \\
	Teaching Fellow, Physics, Boston University \\  
	Courses taught: Recitation sections for Electricity and Magnetism, recitation and lab sections for Modern Physics (undergraduate). Guest lectures in Modern Physics.  \\
	Courses graded: Mathematical Methods (undergraduate), Computational Physics, Statistical Mechanics II, Solid State Physics (graduate)   
	\item \textbf{2003-2005}\\
	Teaching Assistant, Physics, University of Rhode Island \\  
	Courses taught: Lab sections for Introductory Mechanics   \\
	Skills: Assisted in maintenance of instructional lab equipment.  Developed new lab manual for Introductory Mechanics classes, focusing on clear exposition for use by new teaching assistants, and pedagogical value for students.  Arranged technology demonstrations for new graduate students. 
	\item \textbf{2002-2003}\\
	Integrated Science Teacher, Evergreen Valley High School, San Jose, CA  \\
	Courses taught: Advisory and four sections of sophomore level integrated science.\\  
	Skills: Assisted in the opening of a new school, ordering and preparing equipment and supplies for labs, developing curriculum for Advisory and for Integrated Science. Made heavy use of educational technology in a school that provided laptops for every student, serving a diverse student population.  
	\item \textbf{1999-2002} \\
	Teaching Assistant, San Francisco State University \\  
	Courses taught: Critical Thinking  \\
	Courses assisted: Logic, Philosophy of Science (undergraduate), and Philosophy of Science (graduate)  \\
	Courses graded: Ancient Philosophy and Medieval Philosophy (undergraduate) \\  
	Skills: Developed online course material and organized large tutorial sessions for Logic and Philosophy of Science.  Developed curriculum for Critical Thinking, serving a diverse student population.  
	\item \textbf{1999-2002} \\
	Substitute Teacher, San Francisco Public Schools \\  
	Worked in a wide variety of public high schools and middle schools, serving classes in the sciences, mathematics, and history.  Served the diverse student populations of San Francisco.  
	\item \textbf{1998-1999} \\
	Math Teacher, East Union High School, Manteca, CA \\  
	Courses taught: College-prep Algebra and standard Algebra \\  
	Skills: Used a variety of group learning and direct instruction techniques, assisted in the preparation of the school's accreditation review with the Western Association of Schools and Colleges, assistant coach of the varsity soccer team.  
	\item \textbf{1998} \\
	Summer Research Program, Lawrence Livermore National Laboratory \\
	Skills: Assisted in design calculations for construction of the Intense-Electron Beam Ion Trap (I-EBIT).  Finite element modelling, simulation of ion focusing lenses.  \\
	Supervisor: Ross Marrs
\end{itemize}

\section*{Publications}
\subsection*{Peer Reviewed}
\begin{itemize}
	\item Urbanc, B., \textbf{M. Betnel}, L. Cruz, G. Bitan, D. Teplow.  
\emph{Elucidation of Amyloid $\beta$-Protein Oligomerization Mechanisms: Discrete Molecular Dynamics Study}, Journal of the American Chemical Society  132 (4266), 2010.     
	\item \textbf{M. Nelson}, \emph{Moral agency in a propaganda system}, Discourse 8, 2002.
\end{itemize}

\subsection*{Manuscripts in preparation}
\begin{itemize}
	\item Urbanc, B., \textbf{M. Betnel}, H. Li, E. Fradinger, B.H. Monien, G. Bitan  
	\emph{In silico study of A$\beta_{1 − 42}$ oligomer formation in the presence of 
	A$\beta$-derived toxicity inhibitors relevant to Alzheimer's disease}.  
	In preparation.  
	\item \textbf{Betnel, M.}, N.V. Dokholyan, B. Urbanc.  
	\emph{From disordered amyloid $\beta$-proteins to soluble oligomers and 
	protofibrils using Discrete Molecular Dynamics}.  
	Invited review, in preparation.  
	\item \textbf{Betnel, M.}, L. Cruz, B. Wolozin, G. Bitan, B. Urbanc.  
	\emph{$\alpha$-Synuclein Folding and Oligomer Formation: Discrete Molecular Dynamics Study}.  
	In preparation.  
	\item \textbf{Betnel, M.}, L. Cruz, G. Bitan, B. Urbanc  
	\emph{Free-energy landscape for folding of amyloid $\beta$ monomers 
	in the presence of A$\beta$-derived toxicity inhibitors}.  
	In preparation.  
	\item \textbf{Betnel, M.}, B. Urbanc. 
	\emph{Determination of free energy landscapes for folding of 
	unstructured proteins}.
	In preparation.  
\end{itemize}


\subsection*{Other Publications}
\begin{itemize}
	\item \textbf{M. Nelson}, \emph{Introductory Laboratory Manual, Physics 111-112}.  University of Rhode Island Department of Physics,  2004.
\end{itemize}

\subsection*{Invited Talks}
\begin{itemize}
	\item  "Computational study of protein folding and assembly in
          Alzheimer's disease". \emph{Brown University, Department of
            Physics}, Providence, RI. December 15, 2010.
          \item  "Moral agency in a propaganda system". \emph{St. Thomas Episcopal Church}, Sunnyvale,
            CA. January 10, 2002.
\end{itemize}



\subsection*{Posters}
\begin{itemize}
	\item \textbf{Betnel, M.}, L. Cruz, B. Wolozin, B. Urbanc.  
	"Computational study of $\alpha$-synuclein protein folding and assembly in Parkinson's disease". \emph{Protein Society 23rd Symposium}, Boston, MA.  July 2010.
	\item \textbf{Betnel, M.}, L. Cruz, B. Wolozin, B. Urbanc.  
	"Computational studies of protein folding and aggregation in Parkinson's 
	disease". \emph{American Chemical Society 238th National Meeting}, Washington, DC.  August, 2010.
\end{itemize}

\section*{Awards and grants}
\begin{itemize}
	\item TeraGrid Research allocation, \emph{Multiscale Molecular Dynamics of Protein
	 Folding and Assembly}, with B. Barz and B. Urbanc, Drexel University, 
	June 2010.
    \item TeraGrid Startup allocation, \emph{Elucidation of the free energy folding 
landscapes of amyloid $\beta$-protein and $\alpha$-synuclein, relevant to 
Alzheimer's and Parkinson's diseases}, with B. Urbanc, Drexel University, 
February 2010.  
	\item Teaching Fellow of the Year, Boston University Department of Physics, 2007.

\end{itemize}


\section*{Affiliations}
\begin{itemize}
	\item American Physical Society
	\item American Association of Physics Teachers
	\item American Chemical Society
	\item The Protein Society
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
